A Novel Model-Free Actor-Critic Reinforcement Learning Approach for Dynamic Target Tracking

### 2020-07-10 paperMIC2020/paperIEEE-MIC2020-V1.tex
cleaned and removed pdf
add refrences

Tracking a random moving target using a mobile robot is a key problem and a fundamental feature in autonomous robots operating in areas such as surveillance, search and rescue missions, environmental monitoring, household cleaning, to name a few~\cite{kolling2006,Encarnacao2001,Ju2001,Kitowski2012,Zhang2013}. Throughout the years, the dynamic target tracking problem has received a profound amount of research in academia and industry\todo{Add 2 recent references}. This is mainly due to their inherent complex nonlinear dynamics. Most of the target tracking algorithms proposed in the literature either rely on A) mathematical and kinematic models of both the robot and the target \cite{Huang2008}, B) the assumption that the target or its trajectory are static and known a priori, and C) nonlinear control or soft-computing techniques that are driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity \cite{KD2007,Cren2017}. In a typical tracking problem, a robot is to apply a local control actions that enable it to maintain a relative position and orientation from the designated target while following a certain trajectory. It can also be applied on a fleet of robots where multiple robots maintain a geometric configuration relative to the target\cite{Oh2015-Survey,Liu2017-Modular}.

@@

 where $\ell_a$ is the actor learning rate.  The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm~\ref{alg:ModelFreeTracking}. \todo[inline]{In Algorithm 1, add a line with $n=2$ (state error dimension) and $m=2$ (input dimension)} %

>>>>

Tracking a random moving target using a mobile robot is a key problem and a fundamental feature in autonomous robots operating in areas such as surveillance, search and rescue missions, environmental monitoring, household cleaning, to name a few~\cite{kolling2006,Encarnacao2001,Ju2001,Kitowski2012,Zhang2013}. Throughout the years, the dynamic target tracking problem has received a profound amount of research in academia and industry \cite{wei2018}, \cite{liu2019}  . This is mainly due to their inherent complex nonlinear dynamics. Most of the target tracking algorithms proposed in the literature either rely on A) mathematical and kinematic models of both the robot and the target \cite{Huang2008}, B) the assumption that the target or its trajectory are static and known a priori, and C) nonlinear control or soft-computing techniques that are driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity \cite{KD2007,Cren2017}. In a typical tracking problem, a robot is to apply a local control actions that enable it to maintain a relative position and orientation from the designated target while following a certain trajectory. It can also be applied on a fleet of robots where multiple robots maintain a geometric configuration relative to the target\cite{Oh2015-Survey,Liu2017-Modular}.

@@

 where $\ell_a$ is the actor learning rate.  The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm~\ref{alg:ModelFreeTracking}. 
